---
title: "SurvivalAnalysisScript.R"
output: html_notebook
---

```{r}
library(readxl)
library(survival)
library(survminer)
library(dplyr)
library(ComplexHeatmap)
library(circlize)
#palette 
dred='#C72228'
dorange='#F98F34'
dblue='#0C4E9B'
dgreen='#6BBC46'
dmred='#C72026'
dmorange='#F98E31'
dmblue='#0B4E9B'
dmgreen='#69BC42'
lred='#F5867F'
lorange='#FFBC80'
lblue='#6B98C4'
lgreen='#B4DEA2'
two_pal=c(dblue,dred)
three_pal=c(dred,dorange,dblue)

#Figure 1E
data <-read.table(".\\data\\Hi-SECURE_construction\\Seracare_Standards_SiteAF.xls",sep="\t",header=T,row.names=1)
group<-read.table(".\\data\\Hi-SECURE_construction\\Seracare_Standards_Group.xls",sep="\t",head=T)
data1 <- data[,1:5]
data2 <- data[,6:9]
data3 <- data[,10:13]
data4 <- data[,14:18]
data5 <- data[,19:23]
group1 <- group[group$Type=="ctDNA-0%",]
group2 <- group[group$Type=="ctDNA20ng-0.005%",]
group3 <- group[group$Type=="ctDNA40ng-0.005%",]
group4 <- group[group$Type=="ctDNA-0.05%",]
group5 <- group[group$Type=="ctDNA-0.5%",]
df1=data.frame(ctDNA=group1$Type)
rownames(df1)=group1$Sample
ha1 = HeatmapAnnotation(df = df1, col = list(ctDNA = c("ctDNA-0%" = "#6B98C4","ctDNA20ng-0.005%" = "#C72228","ctDNA40ng-0.005%" = "#0C4E9B", "ctDNA-0.05%" = "#F98F34","ctDNA-0.5%" = "#6BBC46")),show_legend =TRUE,show_annotation_name = FALSE,annotation_height = 0.2)
df2=data.frame(ctDNA=group2$Type)
rownames(df2)=group2$Sample
ha2 = HeatmapAnnotation(df = df2, col = list(ctDNA = c("ctDNA-0%" = "#6B98C4","ctDNA20ng-0.005%" = "#C72228","ctDNA40ng-0.005%" = "#0C4E9B", "ctDNA-0.05%" = "#F98F34","ctDNA-0.5%" = "#6BBC46")),show_legend =TRUE,show_annotation_name = FALSE,annotation_height = 0.2)
df3=data.frame(ctDNA=group3$Type)
rownames(df3)=group3$Sample
ha3 = HeatmapAnnotation(df = df3, col = list(ctDNA = c("ctDNA-0%" = "#6B98C4","ctDNA20ng-0.005%" = "#C72228","ctDNA40ng-0.005%" = "#0C4E9B", "ctDNA-0.05%" = "#F98F34","ctDNA-0.5%" = "#6BBC46")),show_legend =TRUE,show_annotation_name = FALSE,annotation_height = 0.2)
df4=data.frame(ctDNA=group4$Type)
rownames(df4)=group4$Sample
ha4 = HeatmapAnnotation(df = df4, col = list(ctDNA = c("ctDNA-0%" = "#6B98C4","ctDNA20ng-0.005%" = "#C72228","ctDNA40ng-0.005%" = "#0C4E9B", "ctDNA-0.05%" = "#F98F34","ctDNA-0.5%" = "#6BBC46")),show_legend =TRUE,show_annotation_name = FALSE,annotation_height = 0.2)
df5=data.frame(ctDNA=group5$Type)
rownames(df5)=group5$Sample
ha5 = HeatmapAnnotation(df = df5, col = list(ctDNA = c("ctDNA-0%" = "#6B98C4","ctDNA20ng-0.005%" = "#C72228","ctDNA40ng-0.005%" = "#0C4E9B", "ctDNA-0.05%" = "#F98F34","ctDNA-0.5%" = "#6BBC46")),show_legend =TRUE,annotation_height = 0.2)
col_fun = colorRamp2(c(0,0.001, 0.05, 0.5), c("white", "#F98F34","#F5867F", "#C72228"),transparency = 0.3)
ht1 = Heatmap(data1, show_row_names = FALSE, show_column_names = TRUE,top_annotation = ha1, show_heatmap_legend=FALSE,col= col_fun, column_title ="", show_row_dend=TRUE,row_dend_side ="left",cluster_rows = TRUE,cluster_columns = FALSE)
ht2 = Heatmap(data2, show_row_names = FALSE, show_column_names = TRUE,top_annotation = ha2, show_heatmap_legend=FALSE,col= col_fun, column_title ="", show_row_dend=F,cluster_columns = FALSE)
ht3 = Heatmap(data3, show_row_names = FALSE, show_column_names = TRUE,top_annotation = ha3, show_heatmap_legend=FALSE,col= col_fun, column_title ="", show_row_dend=F,cluster_columns = FALSE)
ht4 = Heatmap(data4, show_row_names = FALSE, show_column_names = TRUE,top_annotation = ha4, show_heatmap_legend=FALSE,col= col_fun, column_title ="", show_row_dend=F,cluster_columns = FALSE)
ht5 = Heatmap(data5, show_row_names = TRUE, show_column_names = TRUE,top_annotation = ha5,row_names_gp = gpar(fontsize = 10),col= col_fun,name = " ", column_title ="", show_row_dend=F, heatmap_legend_param = list(color_bar = "continuous"),cluster_columns = FALSE)
#pdf(file="Seracare.heatmap.pdf",width=15,height=12)
draw(ht1 + ht2 + ht3 + ht4+ht5,gap = unit(c(1.5,1.5,1.5,1.5,0), "mm"))
#dev.off()

```
```{r}
#Figure 3F
data <- read_excel(".\\data\\Hi-SECURE_construction\\\\Clinical.xlsx",sheet = 1) %>% filter(PatientID!= "M151") 
data_luad=data %>% filter(Subtype == "LUAD") %>% mutate(TNM_Shedder = paste0("TNM=",TNM, ",Shedder=", Shedder))
fontsize<-12

#pdf(".\\Figure\\Hi_secure_Pre.pdf",width = 5,height = 5,onefile = FALSE)
dat <- data %>% select(PatientID,RFS.status,RFS,Hi_secure_Pre_operation)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = levels(group)[1]
level2_num = levels(group)[2]
survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

p.val = 1 - pchisq(data.survdiff$chisq, length(data.survdiff$n) - 1)
HR = (data.survdiff$obs[2]/data.survdiff$exp[2])/(data.survdiff$obs[1]/data.survdiff$exp[1])
up95 = exp(log(HR) + qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
low95 = exp(log(HR) - qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
HR <- paste("HR = ", round(HR,2),"[",round(low95,2),"-", round(up95,2) ,"]",sep = "")

plot <- ggsurvplot(fit, data = survival_dat, 
                   conf.int = F, 
                   linetype = c(1,1),
                   palette = two_pal, 
                   legend.title = "HI-Secure Pre-operation",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text= F, 
                   legend.labs = c(level1_num,level2_num),
                   pval = paste(pval = ifelse(p.val < 0.001,"p < 0.001",paste("p = ",round(p.val,3), sep = "")),
                                HR,  sep = "\n"))
print(plot)
#dev.off()
```
```{r}
#Figure 3G
#pdf(paste("Luad_betweenMethod_pre.pdf",sep=""),width = 5,height = 6,onefile = FALSE)
dat <- data_luad %>% select(PatientID,RFS.status,RFS,Pre_operation)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = levels(group)[1]
level2_num = levels(group)[2]
level3_num = levels(group)[3]
survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

p.val = 1 - pchisq(data.survdiff$chisq, length(data.survdiff$n) - 1)
HR = (data.survdiff$obs[2]/data.survdiff$exp[2])/(data.survdiff$obs[1]/data.survdiff$exp[1])
up95 = exp(log(HR) + qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
low95 = exp(log(HR) - qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
HR <- paste("HR = ", round(HR,2),"[",round(low95,2),"-", round(up95,2) ,"]",sep = "")

plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   linetype = c(1,1,1),
                   palette =c("#C72228","#F98F34","#0C4F9B"), 
                   legend.title = "LUAD Pre-operation",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num,level3_num),
                   pval = paste(pval = ifelse(p.val < 0.001,"p < 0.001",paste("p = ",round(p.val,3), sep = "")),
                                HR,  sep = "\n"))
print(plot)
#dev.off()

```

```{r}
#Figure 3H
data <- read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1)%>% filter(PatientID!= "M151" & Subtype=='LUAD') %>% mutate(shedder_egfr = paste0(Shedder, EGFR))
data_I<-data%>% filter(Stage== "I" )    
data_III<-data%>% filter(Stage_actual== "III" )              
data1 <- data_I
data1 <- as.data.frame(data1)
dat <- data1 %>% select(PatientID,RFS.status,RFS,shedder_egfr)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = paste0(levels(group)[1], "(", length(group[group == levels(group)[1]]), ")")
level2_num = paste0(levels(group)[2], "(", length(group[group == levels(group)[2]]), ")")
level3_num = paste0(levels(group)[3], "(", length(group[group == levels(group)[3]]), ")")
level4_num = paste0(levels(group)[4], "(", length(group[group == levels(group)[4]]), ")")

survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

#pdf("LUAD_Shedder_EGFR_I.pdf",width = 6,height =7.5,onefile = FALSE)

plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   linetype = c(2,1,2,1),
                   palette = c(dblue,dmblue,dmred,dred), 
                   legend.title = "LUAD TNM-I",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num,level3_num,level4_num),
  )
print(plot)
#dev.off()
```


```{r}
#Figure 4A
data <- read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1)%>% filter(Therapy!= "Yes")
#pdf("Hi_secure_post1M.pdf",width = 5,height = 5,onefile = FALSE)
dat <- data %>% select(PatientID,RFS.status,RFS,Hi_secure_Post1M)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = levels(group)[1]
level2_num = levels(group)[2]
survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

p.val = 1 - pchisq(data.survdiff$chisq, length(data.survdiff$n) - 1)
HR = (data.survdiff$obs[2]/data.survdiff$exp[2])/(data.survdiff$obs[1]/data.survdiff$exp[1])
up95 = exp(log(HR) + qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
low95 = exp(log(HR) - qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))

plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   linetype = c(1,1),
                   palette = two_pal, 
                   legend.title = "HI-Secure Post1M",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num),
                   pval = paste(pval = ifelse(p.val < 0.001,"p < 0.001",paste("p = ",round(p.val,3), sep = "")),
                                 sep = "\n"))
print(plot)
dev.off()

```
```{r}
#Figure 4C
data1 <-read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1) %>% filter(PatientID != "M151") %>% mutate(Pre_Post = paste0(Hi_secure_Pre_operation, "_", Hi_secure_Post1M))
data1 <- as.data.frame(data1)

dat <- data1 %>% select(PatientID,RFS.status,RFS,pre_post)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")

my.surv = Surv(dat$time, dat$state)

group = as.factor(dat[,4])
level1_num = paste0(levels(group)[1], "(", length(group[group == levels(group)[1]]), ")")
level2_num = paste0(levels(group)[2], "(", length(group[group == levels(group)[2]]), ")")
level3_num = paste0(levels(group)[3], "(", length(group[group == levels(group)[3]]), ")")

survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

p.val = 1 - pchisq(data.survdiff$chisq, length(data.survdiff$n) - 1)
HR = (data.survdiff$obs[2]/data.survdiff$exp[2])/(data.survdiff$obs[1]/data.survdiff$exp[1])
up95 = exp(log(HR) + qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
low95 = exp(log(HR) - qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
CI <- paste("95% CI: ", paste(round(low95,2), round(up95,2), sep = " - "), sep = "")

#pdf("Pre_post1m_threetype.pdf",width = 5,height =6.5,onefile = FALSE)
plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   #censor = F, 
                   linetype = c(1,1,1),
                   palette = c(dred,dblue,dorange), 
                   legend.title = "HI-Secure Pre",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num,level3_num),
                   pval = paste(pval = ifelse(p.val < 0.001,"p < 0.001",paste("p = ",round(p.val,3), sep = "")),
                                 sep = "\n"))
print(plot)
#dev.off()
```
```{r}
data_pb <- read_excel(".\\data\\POEM\\TNM_PB.xlsx",sheet = 1) %>%  filter(PatientID != "M151") 
data1 <- data_pb
data1 <- as.data.frame(data1)
dat <- data1 %>% select(PatientID,RFS.status,RFS,stage)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])

level1_num = paste0(levels(group)[1], "(", length(group[group == levels(group)[1]]), ")")
level2_num = paste0(levels(group)[2], "(", length(group[group == levels(group)[2]]), ")")
level3_num = paste0(levels(group)[3], "(", length(group[group == levels(group)[3]]), ")")
level4_num = paste0(levels(group)[4], "(", length(group[group == levels(group)[4]]), ")")
level5_num = paste0(levels(group)[5], "(", length(group[group == levels(group)[5]]), ")")
level6_num = paste0(levels(group)[6], "(", length(group[group == levels(group)[6]]), ")")
survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

#pdf("TNM_VS_PB.pdf",width = 7,height =7.5,onefile = FALSE)

plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   #censor = F, 
                   linetype = c(1,1,1,3,3,3),
                   palette = c(dblue,dorange,dred,dmblue,dmorange,dmred), 
                   legend.title = "TNM vs. PB",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   #risk.table = T, ## 所有可用的value是TRUE, FALSE, 'absolute', 'percentage', 'nrisk_cumcensor', 'nrisk_cumevents' 
                   #risk.table.y.text.col = T, ## risk table左侧是否用对应分层变量的颜色注释
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num,level3_num,level4_num,level5_num,level6_num))
print(plot)
#dev.off()
```
```{r}
#Figure 4E
data_pb <- read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1) 
clinical <- read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1) %>% filter(PatientID != "M151")
dat1<-data_pb%>%  filter(PB == "I")
dat2<-data_pb%>%  filter(PB == "II_III")
dat2 <- data_pb %>%
  filter(PB == "II" | PB == "III")

data1 <- dat1
data1 <- as.data.frame(data1)
dat1 <- data1 %>% select(PatientID,RFS.status,RFS,Therapy)
dat1 <- as.data.frame(dat1)

data2 <- dat2
data2 <- as.data.frame(data2)
dat2 <- data2 %>% select(PatientID,RFS.status,RFS,Therapy)
dat2<- as.data.frame(dat2)

bcMatched2<- read.csv(".\\data\\POEM\\Clinical_After_PSM.csv") 
dat11=dat1%>%  filter(PatientID %in% bcMatched2$PatientID)
dat<-dat11
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = levels(group)[1]
level2_num = levels(group)[2]

survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

p.val = 1 - pchisq(data.survdiff$chisq, length(data.survdiff$n) - 1)
HR = (data.survdiff$obs[2]/data.survdiff$exp[2])/(data.survdiff$obs[1]/data.survdiff$exp[1])
up95 = exp(log(HR) + qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
low95 = exp(log(HR) - qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
HR <- paste("HR = ", round(HR,2),"[",round(low95,2),"-", round(up95,2) ,"]",sep = "")

#pdf("PB_I_therapy.pdf",width = 5,height =5,onefile = FALSE)

plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   #censor = F, 
                   linetype = c(1,1),
                   palette = c(dorange,dgreen), 
                   legend.title = "PB-I Therapy",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num),
                   pval = paste(pval = ifelse(p.val < 0.001,"p < 0.001",paste("p = ",round(p.val,3), sep = "")),
                                HR,  sep = "\n"))
print(plot)
#dev.off()
```
```{r}
#Figure 4F
dat22=dat2%>%  filter(PatientID %in% bcMatched2$PatientID)
dat<-dat22
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = levels(group)[1]
level2_num = levels(group)[2]
survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

p.val = 1 - pchisq(data.survdiff$chisq, length(data.survdiff$n) - 1)
HR = (data.survdiff$obs[2]/data.survdiff$exp[2])/(data.survdiff$obs[1]/data.survdiff$exp[1])
up95 = exp(log(HR) + qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
low95 = exp(log(HR) - qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
HR <- paste("HR = ", round(HR,2),"[",round(low95,2),"-", round(up95,2) ,"]",sep = "")

#pdf("PB_II_III_therapy.pdf",width = 5,height =5,onefile = FALSE)

plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   linetype = c(1,1),
                   palette = c(dorange,dgreen), 
                   legend.title = "PB-II_III Therapy",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num),
                   pval = paste(pval = ifelse(p.val < 0.001,"p < 0.001",paste("p = ",round(p.val,3), sep = "")),
                                HR,  sep = "\n"))
print(plot)
#dev.off()
```
```{r}
#Fiugre5A
data <-read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1)  %>% filter(Hi_secure_Landmark!= "")  %>% mutate(Subtype_landmark = paste0(Subtype, Hi_secure_Landmark),stage_landmark=paste0(Stage, Hi_secure_Landmark))
data_ct<-data %>% filter(TherapyType== "CT" |TherapyType== "CT+ICI" |TherapyType== "CT+TKI" ) 
data_luad=data %>% filter(Subtype == "LUAD") %>% mutate(TNM_Shedder = paste0("TNM=",TNM, ",Shedder=", Shedder))
data_post1m_positive=data %>% filter(Hi_secure_Post1M == "Positive")
data_post1m_negative=data %>% filter(Hi_secure_Post1M == "Negative")
data_post1m_therapy=read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1)  %>% filter(PatientID!= "M151") %>% mutate(post1M_therapy = paste0(Hi_secure_Post1M, Therapy))

#pdf("Hi_secure_Landmark.pdf",width = 5,height = 5,onefile = FALSE)
dat <- data %>% select(PatientID,RFS.status,RFS,Hi_secure_Landmark)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = levels(group)[1]
level2_num = levels(group)[2]
survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

p.val = 1 - pchisq(data.survdiff$chisq, length(data.survdiff$n) - 1)
HR = (data.survdiff$obs[2]/data.survdiff$exp[2])/(data.survdiff$obs[1]/data.survdiff$exp[1])
up95 = exp(log(HR) + qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
low95 = exp(log(HR) - qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
HR <- paste("HR = ", round(HR,2),"[",round(low95,2),"-", round(up95,2) ,"]",sep = "")

plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   linetype = c(1,1),
                   palette = two_pal, 
                   legend.title = "HI-Secure Landmark",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num),
                   pval = paste(pval = ifelse(p.val < 0.001,"p < 0.001",paste("p = ",round(p.val,3), sep = "")),
                                HR,  sep = "\n"))
print(plot)
#dev.off()
```
```{r}
#Figure 5D
data <- read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1)  %>% filter(Hi_secure_Post1M!= "")  
data_ct<-data %>% filter(TherapyType== "CT" |TherapyType== "CT+ICI" |TherapyType== "CT+TKI" ) 
#pdf("CT_Post1M.pdf",width = 5,height = 6,onefile = FALSE)
dat <- data_ct %>% select(PatientID,RFS.status,RFS,Hi_secure_Post1M)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = levels(group)[1]
level2_num = levels(group)[2]
survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

p.val = 1 - pchisq(data.survdiff$chisq, length(data.survdiff$n) - 1)
HR = (data.survdiff$obs[2]/data.survdiff$exp[2])/(data.survdiff$obs[1]/data.survdiff$exp[1])
up95 = exp(log(HR) + qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
low95 = exp(log(HR) - qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
HR <- paste("HR = ", round(HR,2),"[",round(low95,2),"-", round(up95,2) ,"]",sep = "")

plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   linetype = c(1,1),
                   palette = two_pal, 
                   legend.title = "Chemo Post1M",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num),
                   pval = paste(pval = ifelse(p.val < 0.001,"p < 0.001",paste("p = ",round(p.val,3), sep = "")),
                                HR,  sep = "\n"))
print(plot)
#dev.off()
```


```{r}
#Figure 5E
data <-read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1)  %>% filter(Hi_secure_Landmark!= "")  
data_ct<-data %>% filter(TherapyType== "CT" |TherapyType== "CT+ICI" |TherapyType== "CT+TKI" ) 
#pdf("CT_Landmark.pdf",width = 5,height = 6,onefile = FALSE)
dat <- data_ct %>% select(PatientID,RFS.status,RFS,Hi_secure_Landmark)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = levels(group)[1]
level2_num = levels(group)[2]
survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

p.val = 1 - pchisq(data.survdiff$chisq, length(data.survdiff$n) - 1)
HR = (data.survdiff$obs[2]/data.survdiff$exp[2])/(data.survdiff$obs[1]/data.survdiff$exp[1])
up95 = exp(log(HR) + qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
low95 = exp(log(HR) - qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
HR <- paste("HR = ", round(HR,2),"[",round(low95,2),"-", round(up95,2) ,"]",sep = "")

plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   #censor = F, 
                   linetype = c(1,1),
                   palette = two_pal, 
                   legend.title = "Chemo Landmark",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num),
                   pval = paste(pval = ifelse(p.val < 0.001,"p < 0.001",paste("p = ",round(p.val,3), sep = "")),
                                HR,  sep = "\n"))
print(plot)
#dev.off()

```


```{r}

#Figure 5F
data <- read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1)   %>% filter(Hi_secure_Longitudinal!= "")  
data_ct<-data %>% filter(TherapyType== "CT" |TherapyType== "CT+ICI" |TherapyType== "CT+TKI" ) 
#pdf("CT_Longitudinal.pdf",width = 5,height = 6,onefile = FALSE)
dat <- data_ct %>% select(PatientID,RFS.status,RFS,Hi_secure_Longitudinal)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = levels(group)[1]
level2_num = levels(group)[2]
survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)

p.val = 1 - pchisq(data.survdiff$chisq, length(data.survdiff$n) - 1)
HR = (data.survdiff$obs[2]/data.survdiff$exp[2])/(data.survdiff$obs[1]/data.survdiff$exp[1])
up95 = exp(log(HR) + qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
low95 = exp(log(HR) - qnorm(0.975)*sqrt(1/data.survdiff$exp[2]+1/data.survdiff$exp[1]))
HR <- paste("HR = ", round(HR,2),"[",round(low95,2),"-", round(up95,2) ,"]",sep = "")

plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   #censor = F, 
                   linetype = c(1,1),
                   palette = two_pal, 
                   legend.title = "Chemo Longitudinal",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level1_num,level2_num),
                   pval = paste(pval = ifelse(p.val < 0.001,"p < 0.001",paste("p = ",round(p.val,3), sep = "")),
                                HR,  sep = "\n"))
print(plot)
#dev.off()
```
```{r}
#Figure 5H
data <- read_excel(".\\data\\POEM\\Clinical.xlsx",sheet = 1)  %>% filter(Hi_secure_Landmark!= "" & Hi_secure_Post1M!="")  %>% mutate(post1m_landmark = paste0(Hi_secure_Post1M, Hi_secure_Landmark))
data_ct<-data %>% filter(TherapyType== "CT" |TherapyType== "CT+ICI" |TherapyType== "CT+TKI" ) 
data_ct$post1m_landmark <- gsub("PositivePositive", "NegativePositive", data_ct$post1m_landmark)

#pdf("CT_Post1M_Landmark.pdf",width = 5,height = 6,onefile = FALSE)
dat <- data_ct %>% select(PatientID,RFS.status,RFS,post1m_landmark)
dat <- as.data.frame(dat)
colnames(dat)[2:4] <- c("state","time","group")
my.surv = Surv(dat$time, dat$state)
group = as.factor(dat[,4])
level1_num = levels(group)[1]
level2_num = levels(group)[2]
level3_num = levels(group)[3]
survival_dat <- data.frame(group = group)
fit <- survfit(my.surv ~ group)
data.survdiff <- survdiff(my.surv ~ group)


plot <- ggsurvplot(fit, data = survival_dat,
                   conf.int = F, 
                   linetype = c(1,1,1),
                   palette = c(dblue,dred,dorange),
                   legend.title = "Chemo Longitudinal",
                   risk.table = TRUE,
                   font.legend = 12,
                   ylab='RFS probability',
                   xlab='Time in months',
                   risk.table.y.text = F, 
                   legend.labs = c(level3_num,level1_num,level2_num))
print(plot)
#dev.off()
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
